Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-23 main.tex
:pencil: Add naive label for backscatter symbol vector

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $c_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with zero-offset (TODO), where the $m$-th constellation point is
			\begin{equation}
				c_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}
			\begin{remark}
				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-PSK corresponds to ideal Intelligent Reflecting Surface (IRS) with $M$ discrete states.
			\end{remark}
		\end{subsection}
	\end{section}

@@

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathbb{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_channel}
			\end{equation}

@@

		\begin{subsection}{Signal Detection}
			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent AmBC detection scheme \cite{Qian2019} to the multi-tag case and propose a low-complexity energy detection that decodes the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as channel training, instead of being removed by SIC. In other words, the reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of primary link.
			\end{remark}

>>>>

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
			\begin{equation}
				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}
			% Also, define the $M$-PSK constellation set as $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$.

			\begin{remark}
				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-PSK corresponds to ideal Intelligent Reflecting Surface (IRS) with $M$ discrete states.
			\end{remark}
		\end{subsection}
	\end{section}

@@

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq [y[1],\ldots,y[N]]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_channel}
			\end{equation}

@@

		\begin{subsection}{Signal Detection}
			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as in channel training, instead of being removed by SIC.
			\end{remark}

			For the ease of notation, we label the backscatter symbol vector by a decimal number that uniquely maps to the modulation index set. As an example, when tag $k$ is at state $m_k$, the modulation index set is $\{m_1,\ldots,m_K\}$, and the backscatter symbol vector can be defined as $\boldsymbol{c}_l \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T$, where $l \in \{1,\ldots,M^K\}$ in decimal equals $m_1 - 1 \ldots m_{K-1} - 1 \ m_K$ in base-$M$.

			% $\forall k \in \mathcal{K}$, the backscatter symbol vector is $\boldsymbol{c}_l$, where $l$

			% assign the backscatter symbol vector to the corresponding modulation index set, and further label it by the corresponding base-$M$ number.

			% we label the modulation index set $\{m_1,\ldots,m_K\}$ by the corresponding base-$M$ number

			% define the modulation index set as $\{m_1,\ldots,m_K\}$
			% For any backscatter symbol vector $\boldsymbol{c}_l$, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution as

			% Since the status of all tags remain unchanged over $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary symbol $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,
			Since the status of all tags remain unchanged over $N$ primary symbols, the received signal is only subject to the variation of the primary source and AWGN. When the backscatter symbol vector is $\boldsymbol{c}_l$, the received signal at block $n$ follows CSCG distribution as
			\begin{equation}
				y_l[n] \sim \mathcal{CN}\biggl(0,\sigma_l^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2\biggr).
			\end{equation}

			% , and thus follows CSCG distribution. When the backscatter symbol vector is $\boldsymbol{c}_l$,

			% any backscatter symbol vector

			% , and thus follows CSCG distribution as

			% the received
